Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-10-08 paper/paper.tex
Move around a bit

\begin{figure}[p]

@@

and SAT solvers, and the final shows the number of search nodes used on the clique
encoding.}\label{figure:alt}

@@

The pseudo-boolean (PB) encoding is as follows. For each pattern vertex $v$ and each target vertex
$w$, we have a binary variable which takes the value 1 if and only if $v$ is mapped to $w$.
Constraints are added to ensure that each pattern vertex maps to exactly one target vertex, that
each target vertex is mapped to by at most one pattern vertex, that adjacent vertices are mapped to
adjacent vertices, and that non-adjacent vertices are mapped to non-adjacent vertices. We used the
Clasp solver~\citep{gekakaosscsc11a} version 3.1.3 to solve the pseudo-boolean instances.  The
instances that are hard for the Glasgow solver remain hard for the PB solver, including instances
inside the central region, and the easy satisfiable instances remain easy. Similar results were
seen with the Glucose SAT solver \cite{glucose} using a direct encoding of the cardinality constraints. (We also
implemented an integer program encoding; the Gurobi solver was only able to solve some of the
trivial satisfiable instances, and was almost never able to prove unsatisfiability within the time
limit.)

>>>>

@@

and SAT solvers, the fifth shows the number of search nodes used on the clique encoding, and the
final row the MIP encoding.}\label{figure:alt}

@@

The pseudo-boolean (PB) encoding is as follows. For each pattern vertex $v$ and each target vertex
$w$, we have a binary variable which takes the value 1 if and only if $v$ is mapped to $w$.
Constraints are added to ensure that each pattern vertex maps to exactly one target vertex, that
each target vertex is mapped to by at most one pattern vertex, that adjacent vertices are mapped to
adjacent vertices, and that non-adjacent vertices are mapped to non-adjacent vertices. We used the
Clasp solver~\citep{gekakaosscsc11a} version 3.1.3 to solve the pseudo-boolean instances.  The
instances that are hard for the Glasgow solver remain hard for the PB solver, including instances
inside the central region, and the easy satisfiable instances remain easy. Similar results were seen
with the Glucose SAT solver \cite{glucose} using a direct encoding of the cardinality constraints.
We also implemented an integer program encoding: the Gurobi solver was only able to solve some of
the trivial satisfiable instances, and was almost never able to prove unsatisfiability within the
time limit.
